An introduction to pglmm in lme4

### 2021-01-29 response.md

Thank you for submitting your research to MEE and apologies for the long time getting back to you, which partly a consequence of the ongoing lock-down work-from-home situation. Your manuscript has been reviewed by two highly qualified reviewers who found your work interesting while raising several points about the presentation and extent of the simulations, the scalability of the method and suggesting the inclusion of empirical examples. Based on the reviewers’ judgment and my own take on the paper I cannot recommend the acceptance of this paper at this point, but would encourage you to resubmit a thoroughly re-worked version.

**MLi: Thank you for letting us resubmit.**

As currently presented I found this paper a little bit in between an application note and a research paper but lacking some key components from both, but turning it into a research paper would require, in my opinion, the addition of an empirical example (see also comments from reviewer 1).

**MLi: This paper is intended as an application/software paper.** 
**TODO: didn't we already do this? We have included the example provided in Chapter 11 Garamszegi (DONE) in our release branch. We can add Li et al. Dune mellow example if we want, however, one of the reason we went through the trouble is because we found some bugs in their example with phylo-interactions.**

@@

- In the same spirit of applied statistics, a brief description (or table) of which functions to use in the libraries lme4 and glmmTMB to make these models work would make it easier to start. There should also be mention of the tutorial available in the repository

**MLi: we have now added a tutorial**

- It would also be beneficial to add an application of the method with biological data directly in the article. The more your article is associated with biological ideas, the more users you will reach in my opinion.

**Going to be a little annoying looking for an example with replicates.**
**Skip?**

### 2021-02-01 vignette.Rmd
updating example

# Basic parameters
nspp <- 3

@@

fitmod <- phylo_lmm2(Y ~ X + (1 |sp) + (1 + X|sp)
			, data=dat 
			, phylonm = "sp" # wishy-washy
			, phyloZ = phyZ # Maybe we just want the phy object and compute this internally
			, nsp = nspp # make default check
			, control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")  ## make default
			, REML = FALSE # make default 
)

>>>>

# Basic parameters
nspp <- 10

@@

fitmod <- phylo_lmm(Y ~ X + (1 + X|sp)
			, data=dat 
			, phylonm = "sp" # wishy-washy
			, phylo = phy
			, phyloZ = phyZ # Maybe we just want the phy object and compute this internally
			# , nsp = nspp # make default check
			, control=lmerControl(check.nobs.vs.nlev="ignore",check.nobs.vs.nRE="ignore")  ## make default
			, REML = FALSE # make default 
)
